Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-25 Paper/paper.tex
Various Changes, added FOTP

\begin{abstract}Internet topology has been measured and modeled for many years, and this topology has been linked to censorship and surveillance. Past studies have not, however, quantified the potential for individual nations to intercept national level Internet paths or analyzed how the evolution of the Internet topology impacts censorship and surveillance. Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

  In this paper, we ask how AS topology has changed over time with respect to national boundaries.  We introduce a new measure, \emph{national chokepoint potential}, to characterize how a country's AS topology is organized in terms of paths that can carry traffic across international borders.  To study country-level chokepoints, we developed \toolname{}, a suite of open source, cross platform, and efficient tools for monitoring national chokepoints on the AS graph.  To illustrate these ideas and tools, we studied how national chokepoint potential correlates with two independent measures of civil liberty, finding a significant relationship between our measure and Internet freedom. \todo[inline]{NEED A RESULT FOR WHAT WE FOUND FOR EVOLUTION OVER TIME}.

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.
\end{abstract}

@@

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move online and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 billion in 2005 to 3.578 billion
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S.\ were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Also, other forms of Internet
tampering such as code injection~\cite{badtraffic,191996} have been observed within the
Internet's backbone. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous online communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}. Several countries
sought to control these movements by disconnecting in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
\todo[inline]{A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.}  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{national chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname{}, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how national chokepoint potential correlates with two independent
measures of civilian liberty, finding \todo[inline]{NEED A RESULT HERE}. \todo[inline]{NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME}.

The paper extends earlier research on AS topology, first by introducing the national chokepoint potential measure, then by presenting open-source cross-platform tools for simulating
and Border Gateway Protocol (BGP) networks, determining chokepoint potential at the country level, and analyzing how this measure has changed over time for certain countries of interest.

@@

We are interested in how AS topologies have changed as the total size of the graph has grown from about 10,000 ASes in the early 2000s to over 60,000 today.
The structural
properties of national AS graphs have evolved differently
from nation to nation whether from economic decision making, infrastructural necessities, or
efforts to build a powerful censorship and surveillance
network.
%The Autonomous Systems (AS) layer of the Internet has grown and changed dramatically over its history.
%The locations and relationships of these ASes determine how many chokepoints
%of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion, together with the changing role of national
governments, points to the importance of understanding properties like
path robustness, AS hierarchies, and the potential for organizations to
control information as it flows in and out of their networks.

@@

%Diverse Censorship Architecture
\par Every nation has a different layout and count of ASes. The
censorship and surveillance strategies of nations also differ. For
instance, China both conducts keyword filtering in border ASes and in
internal provincial ASes \cite{chinafiltering}, while Iran routes its
Internet traffic through a centralized facility \cite{irancensor}.
Having views into the AS topology of a nation, then, will both help
researchers identify nations that could easily conduct censorship and
also provide possible insight into what kind of censorship is likely
being conducted. The measure of chokepoint potential, defined later in
this paper, is a succint way to estimate the important properties of
border ASes related to these capabilities.

% Major Contributions
\par
The primary contributions of our work are as follows: 
\begin{enumerate}
 \item We introduce the measure of chokepoint potential for single border ASes and the aggregate measure national chokepoint potential, 
motivating their value as a way to interpret the capability for a nation to enact censorship or surveillance of its Internet traffic.
 \item We provide an overview of the evolution of national AS-level chokepoints over time, showing how the evolution of the Internet has either facillitated stronger
 AS-level chokepoints or lead to more open flow of information across borders.
 \item We develop a new tool, \toolname{}, that provides the capability for
efficiently evaluating chokepoints for a given state of the Internet. 
 \item we show that national chokepoint potential
has a significant relationship to Internet freedom as measured by two qualitative sources.
\end{enumerate}

% Rest of Paper Layout
\par
The layout of the rest of this paper is as follows: Section 3 provides relavent background information
to the problems we are investigating; Section 4 introduces and defines the measure of chokepoint
potential; Section 5 details our tool for simulating and evaluating AS topologies \toolname{}; Section 6
explains our experimental setups; Sections 7, 8, and 9 provide results, discussion, and related work
respectively.

@@

The AS-layer is the highest level of organization of the Internet, with each individual AS represents a separately administered network, for example, a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes \cite{bgp}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each BGP AS.  These tables express known connections to other ASes and local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

@@

\section{Chokepoint Potential}

@@

Border ASes are ASes that lie one hop from an AS registered to a different country. It stands to reason that if information bottlenecks
were to be implemented by national governments, they would likely be implemented on border ASes. This is not always true, but there are more reasons
to use border ASes as our unit of investigation. For instance, the ratio of the number of border ASes of
a country to all ASes in that country hints toward the abillity of that nation to intercept information flows across their borders.
\figurename \ref{fig:bnodes} shows that globally the number of border ASes has grown at a slower rate to the number of non-border ASes
over time so that the ratio of border ASes to ASes has almost continuously decreased. On the surface it would seem that this fact reflects an ever increasing capability for nations to intercept AS-level paths. This is not
neccessarily the case, however. Because AS-level paths are generated by the distributed BGP and the local preferences of AS administrators often do not
lead to simple shortest path selections, a better way to understand the potential for bottlenecks on border ASes is to investigate the number of BGP generated
paths that pass through each AS. To do this we propose an intuitive measure on border ASes called \emph{chokepoint potential}. Since this is a measure for single ASes
we also need an aggregate measure for comparing nations, which we call \emph{national chokepoint potential}.

@@

\par
Given a set of routing trees, chokepoint potential is an intuitive way to compare individual ASes. With this measure,
the sum of the chokepoint potential for all border ASes for a country is 1.0, as in, all of the border ASes collectively control the
flow of information over the nation's border. To compare one nation to another, we can inspect how many border ASe minimum are required
to obtain a certain chokepoint potential. The more border ASes required, the more difficult it would likely be for that nation to perform
censorship or surveillance, as the government would have to restrict more ISPs, place more filtering hardware, etc. Thus, we can define
another measure, with this one being a national measure. We define the \emph{national chokepoint potential} of a nation to be the minimum number
of ASes required to intercept a selected percentage of AS-level paths. Previous work has used 90\% path interception as a benchmark indicating strong control
of information \cite{throats}, so we use this percentage as well. When used here, however, 90\% path interception indicates a single nation intercepts 90\% of the paths
that either enter said nation (for the out-to-in case) or exit said nation (for the in-to-out case). National chokepoint potential is calculated taking the strongest ASes first,
such that the measure reflects the smallest number of border ASes needed to intercept the paths. We use the number of ASes here and not a percentage because using a percentage would
make it difficult to compare nations. Take for instance the United States, which has many more ASes than most nations. If the United States and another nation both required the same percentage
of border ASes to intercept 90\% of paths, the similarity of these nations would be misleading, because the United States would actually need to control many more ASes.
Our technique provides a comparison more likely to reflect reality.

@@

% Preprocessing and Data pipeline
\toolname{} is a new tool that calculates the chokepoint potential for every border AS given a set of AS relationships.
\toolname{} first takes the entire AS graph, as in from the CAIDA dataset \cite{CAIDA}, and uses the principles of BGPSim \cite{quicksand}
to generate a set of routing trees. These routing trees, as well as a set of AS country codes (for identifying which nation an AS belongs to)
are used to determine the chokepoint potentials for every border AS. Finally, \toolname{} calclates the national chokepoint potential 
for each nation. In our experiments, we used the country codes returned from Team Cymru's
IP to ASN whois service \cite{cymru}. This service only maintains the most recent registration of each AS, so to control for uncertain country to AS links
we keep ASes that have been registered more recently than the current timestam being tested in the path simulation but we do not assign these ASes chokepoint potentials. We chose this route
because the datasets of AS registrations for the various ASN registries tended to have more missing data at specific timestamps.

@@

% Chokepoint calculation
\par
Once BGPSimPy generates the routing trees, they can be processed to determine chokepoint potentials. This is done by iterating over every path between each AS-pair. Because
we use the same random tie-break as BGPSim, there is only 1 path between each AS-pair considered, even if multiple exist in the routing tree. Once a path is determined, it is
traversed. For each AS visited, the number of paths intercepted by that AS is incremented. This is done for both in-to-out paths and out-to-in paths, so only one traversal is
necessary per path. Additionally, the number of paths of each type that belong to each nation is tallied, as this makes up the denominator in equation \ref{eqn:chokePointPotential}.
\toolname{} takes the resulting chokepoint potentials and generates national chokepoint potentials for each nation.

@@

% Chokepoint Evolution
There is ongoing research interest into ASes that intercept large portions of Internet paths \cite{throats}, \cite{decoy}. Some important questions remain unanswered however. For instance, to what
extent does the current state of the Internet support national governments' attempts to censor Internet traffic? How does this vary from nation to nation? Is the Internet developing more
powerful chokepoints, or becoming more evenly accessible?
\par
To probe these questions we first used our chokepoint evaluation technique to investigate the chokepoint potential of all nations for the current Internet as well as the
change in chokepoint potentials over time. We looked at multiple snapshots of AS relationships from the CAIDA dataset (2012-2018).
For each timestamp, we generated routing trees based on these relationships. Then we calculated the chokepoint potential for every border AS per snapshot. As a result we can investigate
how countries have changed overtime in their capability to enact censorship and surveillance. This is an attempt to understand what topological trends have developed historically.
With this test we can compare nations, and see which ones have overtime increased their capability to control the flow of information across their borders.
\par
% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can easily implement censorship, it stands to reason that their might already be a negative relationship between
the chokepoint potential of a nation and its Internet freedom. If a significant relationship were to be found it would strengthen chokepoint potential as a measure of a nation's censorship capability
and it would increase the value in monitoring chokepoint potentials across the globe.
\par
We tested whether a significant relationship exists between our measure of national chokepoints and a qualitative evaluation of Internet Freedom. For Internet Freedom we used
the Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries. Each country receives a numerical score from 0 (the most free)
to 100 (the least free). We compare our results to the FOTN scores by ranking nations according to national chokepoint potential, particulary the number of border ASes required to intercept
90\% of paths for each nation and viewing these rankings against the FOTN scores.

@@

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in \figurename \ref{fig:nodesFree} and \figurename \ref{fig:nodesCensor}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Iran) as well as the increase for other nations
(Germany and France). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.

@@

In our test of the relationship between Internet Freedom and national chokepoint potential, we plotted the Freedom on the Net score
of each nation vs the number of border ASes that that nation needed to in order to intercept 90\% of in-to-out paths. Additionally,
we evaluated the relationship with an Ordinarly Least Squares (OLS) fit, and found that the relationship was statistically significant,
with a p-value $\leq$ 0.002 for 2017. The relationship held for other timestamps as well. The results for 2017 are shown in figure \ref{fig:fotn2017}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\caption{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017). 
	Green nations are free, yellow are mostly free, and blue are not free according to FOTN.}\label{fig:fotn2017}
\end{figure}

@@

\section{Discussion}

% Chokepoint Potential
In this paper we have introduced a novel measure, chokepoint potential, that allows us to
evaluate the level of difficulty that a government faces when trying to censor the Internet
based entirely on AS-level topology. Our technique for evaluating chokepoint potential using
\toolname{} provides a monitoring capability of BGP dynamics that was previously not possible.
We have taken advantage of efficient simulation, standard AS relationship datasets, and cross-platform
design principles so that this tool is readily deployable for future research.
% Ecolution over time
\par
Our application of \toolname{} to investigate evolutions in the global AS graph over time shows us
interesting trends in AS topologies.
% Internet Freedom
\par
We have validated chokepoint potential as having a relationship to actual censorship by showing
the significance of the relationship between the chokepoint potential of nations and their FOTN
score from freedom house.

>>>>

% \begin{abstract}Internet topology has been measured and modeled for many years, and this topology has been linked to censorship and surveillance. Past studies have not, however, quantified the potential for individual nations to intercept national level Internet paths or analyzed how the evolution of the Internet topology impacts censorship and surveillance. Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

%   In this paper, we ask how AS topology has changed over time with respect to national boundaries.  We introduce a new measure, \emph{national chokepoint potential}, to characterize how a country's AS topology is organized in terms of paths that can carry traffic across international borders.  To study country-level chokepoints, we developed \toolname{}, a suite of open source, cross platform, and efficient tools for monitoring national chokepoints on the AS graph.  To illustrate these ideas and tools, we studied how national chokepoint potential correlates with two independent measures of civil liberty, finding a significant relationship between our measure and Internet freedom. \todo[inline]{NEED A RESULT FOR WHAT WE FOUND FOR EVOLUTION OVER TIME}.

% This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
% path simulation and routing tree datasets to view snapshots of the Internet
% over multiple years. We provide comprehensive and accessible tools for studying
% the complex and dynamic AS level Internet topology. Through this approach we
% can more carefully evaluate the state of the Internet than was previously possible.
% \end{abstract}

\begin{abstract}
	Internet topology has been measured and modeled for many years, and this topology has been linked to 
	censorship and surveillance. Past studies have not, however, quantified the potential for individual 
	nations to intercept national level Internet paths or analyzed how the evolution of the Internet 
	topology impacts censorship and surveillance. We introduce a new measure, \emph{national breakthrough
	potential}, or NBP, to characterize how a country's AS topology is organized in terms of paths that can carry 
	traffic across international borders.  To study country-level chokepoints, we developed \toolname{}, a 
	suite of open source, cross platform, and efficient tools for monitoring national chokepoints on the 
	AS graph. 
	We find that for many nations the continuous growth of the AS graph is not reflected by a more open
	flow of information across national borders, and in fact for nations known to conduct censorship we
	identify a trend toward strengthening chokepoints. Additionally, we find that a significant 
	relationship exists between NBP and Internet freedom as evaluated from two qualitative sources.
\end{abstract}

@@

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move online and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 billion in 2005 to 3.578 billion
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S.\ were recently overturned, and large
content services are under enormous pressure to 'do
something' about fake news and bad actors. Also, other forms of Internet
tampering such as code injection~\cite{badtraffic,191996} have been observed within the
Internet's backbone. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous online communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}. Several countries
sought to control these movements by disconnecting in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
\todo[inline]{A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.}

\par
In this paper, we focus on the Autonomous Systems (AS) level of the Internet.
Autonomous Systems are groups of routers under common management, such as the network of
a University or an Internet Service Provider (ISP). We apply AS-level topologies to
censorship and surveillance by evaluating border ASes, or ASes that can connect directly to at least
one AS from another nation according to a new measure \emph{chokepoint potential}.
With this measure we can ask how AS topology has changed over time with respect
to national boundaries.  We define \emph{national breakthrough potential} to
measure how a country's AS topology is organized in terms of paths
that can carry traffic across international borders. We developed a
suite of tools, called \toolname{}, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how national chokepoint potential correlates with two independent
measures of civilian liberty, finding that a significan relationship exists between NBP and both liberty measures.
The paper extends earlier research on AS topology, first by introducing the NBP measure, 
then by presenting open-source cross-platform tools for simulating Border Gateway Protocol (BGP) paths,
determining breakthrough potential at the country level, and analyzing how this measure has changed over time for certain countries of interest.

@@

The change in national AS topologies is of interest to censorship research.
The total size of the AS graph (The global network of all ASes) has grown from about 10,000 ASes in the early 2000s to over 60,000 today. 
The structural properties of national subgraphs have evolved differently
from nation to nation whether from economic decision making, infrastructural necessities, or efforts to build a powerful censorship and surveillance
network.
%The Autonomous Systems (AS) layer of the Internet has grown and changed dramatically over its history.
%The locations and relationships of these ASes determine how many chokepoints
%of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion, together with the changing role of national
governments, points to the importance of understanding properties like
path robustness, AS hierarchies, and the potential for organizations to
control information as it flows in and out of their networks.

@@

%Diverse Censorship Architecture
\par Every nation has a different layout and number of ASes, and these national networks
connect to foreign ASes in unique ways. The
censorship and surveillance strategies of nations also differ. For
instance, China both conducts keyword filtering in border ASes and in
internal provincial ASes \cite{chinafiltering}, while Iran routes its
Internet traffic through a centralized facility \cite{irancensor}.
A picture of a nation's censorship or surveillance capabillities then
is not complete without a topological view point.
Having the capabillity to investigate the AS topology of a nation, then, will both help
researchers identify nations that could easily conduct censorship and
also provide possible insight into what kind of censorship is likely
being conducted. Our measure of border ASes, chokepoint potential, defined in detial
in section 3, is a succint way to estimate the important properties of
border ASes related to these capabilities, and our aggregate extension of this measure to
the national level, national breakthrough potential, is an effective way to evaluate and
compare nations and analyze the evolution of the AS-level censorship and surveillance landscape.

% Major Contributions
\par
The primary contributions of our work are as follows: 
\begin{enumerate}
 \item We introduce the measure of chokepoint potential for single border ASes and the aggregate measure national breakthrough potential, 
motivating their value as a way to interpret the capability for a nation to enact censorship or surveillance of its Internet traffic.
 \item We provide an overview of the evolution of national AS-level chokepoints over time, showing how the evolution of the Internet has either facillitated stronger
 AS-level chokepoints or lead to more open flow of information across borders.
 \item We develop a new tool, \toolname{}, that provides the capability for
efficiently evaluating chokepoints for a given state of the Internet. 
 \item We show that national breakthrough potential
has a significant relationship to Internet freedom as measured by two qualitative sources.
\end{enumerate}

% Rest of Paper Layout
\par
The layout of the rest of this paper is as follows: Section 2 provides relavent background information
to the problems we are investigating; Section 3 introduces and defines the measures of chokepoint
potential and national breakthrough potential; Section 4 details our tool for simulating and evaluating AS topologies \toolname{}; Section 5
explains our experimental setups; Sections 6, 7, and 8 provide results, discussion, and related work
respectively.

@@

The AS-layer is the highest level of organization of the Internet, with each individual AS represents a separately administered network, for example, a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes \cite{bgp}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each AS. These tables express known connections to other ASes and local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

@@

\section{Chokepoint Measures}

@@

Border ASes are ASes that lie one hop from an AS registered to a different country. It stands to reason that if information bottlenecks
were to be implemented by national governments, they would likely be implemented on border ASes. This is not always true, but there are more reasons
to use border ASes as our unit of investigation. For instance, the ratio of the number of border ASes of
a country to all ASes in that country hints toward the abillity of that nation to intercept information flows across their borders.
\figurename \ref{fig:bnodes} shows that globally the number of border ASes has grown at a slower rate to the number of non-border ASes
over time so that the ratio of border ASes to ASes has almost continuously decreased. On the surface it would seem that this fact reflects an ever increasing capability for nations to intercept AS-level paths. This is not
neccessarily the case, however. Because AS-level paths are generated by the distributed BGP and the local preferences of AS administrators often do not
lead to simple shortest path selections, a better way to understand the potential for bottlenecks on border ASes is to investigate the number of BGP generated
paths that pass through each AS. To do this we propose an intuitive measure on border ASes called \emph{chokepoint potential}. Since this is a measure for single ASes
we also need an aggregate measure for comparing nations, which we call \emph{national breakthrough potential}.

@@

\par
Given a set of routing trees, chokepoint potential is an intuitive way to compare individual ASes. With this measure,
the sum of the chokepoint potential for all border ASes for a country is 1.0, as in, all of the border ASes collectively control the
flow of information over the nation's border. To compare one nation to another, we can inspect how many border ASe minimum are required
to obtain a certain chokepoint potential. The more border ASes required, the more difficult it would likely be for that nation to perform
censorship or surveillance, as the government would have to restrict more ISPs, place more filtering hardware, etc. Thus, we can define
another measure, with this one being a national measure. We define the \emph{national breakthrough potential} of a nation to be the minimum number
of ASes required to intercept a selected percentage of AS-level paths. Previous work has used 90\% path interception as a benchmark indicating strong control
of information \cite{throats}, so we use this percentage as well. When used here, however, 90\% path interception indicates a single nation intercepts 90\% of the paths
that either enter said nation (for the out-to-in case) or exit said nation (for the in-to-out case). National breakthrough potential is calculated taking the strongest ASes first,
such that the measure reflects the smallest number of border ASes needed to intercept the paths. We use the number of ASes here and not a percentage because using a percentage would
make it difficult to compare nations. Take for instance the United States, which has many more ASes than most nations. If the United States and another nation both required the same percentage
of border ASes to intercept 90\% of paths, the similarity of these nations would be misleading, because the United States would actually need to control many more ASes.
Our technique provides a comparison more likely to reflect reality. This measure is called a breakthrough potential because it indicates the number of border ASes that intercept a vast majority of paths, meaning that a country with high NBP would require controlling many border ASes to prevent a breakthrough, or an unfettered access of
internal ASes to that country.

@@

% Preprocessing and Data pipeline
\toolname{} is a new tool that calculates the chokepoint potential for every border AS given a set of AS relationships as well as the national breakthrough potential
for all nations represented by the AS graph.
\toolname{} first takes the entire AS graph, as in from the CAIDA dataset \cite{CAIDA}, and uses the principles of BGPSim \cite{quicksand}
to generate a set of routing trees. These routing trees, as well as a set of AS country codes (for identifying which nation an AS belongs to)
are used to determine the chokepoint potentials for every border AS. Finally, \toolname{} calclates the national breakthrough potential 
for each nation. In our experiments, we used the country codes returned from Team Cymru's
IP to ASN whois service \cite{cymru} to determine which ASes were registered to which nation. 
This service only maintains the most recent registration of each AS, so to control for uncertain country to AS links
we keep ASes that have been registered more recently than the current timestam being tested in the path simulation but we do not assign these ASes chokepoint potentials. We 
chose this route because the datasets of AS registrations for the various ASN registries tended to have more missing data at specific timestamps.
Fortunately, ASes with registration changes after each test date tend to not be in the AS graph for that test.

@@

% Chokepoint calculation
\par
Once BGPSimPy generates the routing trees, they can be processed to determine chokepoint potentials. This is done by iterating over every path between each AS-pair. Because
we use the same random tie-break as BGPSim, there is only 1 path between each AS-pair considered, even if multiple exist in the routing tree. Once a path is determined, it is
traversed. For each AS visited, the number of paths intercepted by that AS is incremented. This is done for both in-to-out paths and out-to-in paths, so only one traversal is
necessary per path. Additionally, the number of paths of each type that belong to each nation is tallied, as this makes up the denominator in equation \ref{eqn:chokePointPotential}.
\toolname{} takes the resulting chokepoint potentials and generates national breakthrough potentials for each nation.

@@

% Chokepoint Evolution
There is ongoing research interest into ASes that intercept large portions of Internet paths \cite{throats}, \cite{decoy}. Some important questions remain unanswered however. For instance, to what
extent does the current state of the Internet support national governments' attempts to censor Internet traffic? How does this vary from nation to nation? Is the Internet developing more
powerful chokepoints, or becoming more evenly accessible?
\par
To probe these questions we first used our chokepoint evaluation technique to investigate the chokepoint potential of all nations for the current Internet as well as the
change in chokepoint potentials over time. We looked at multiple snapshots of AS relationships from the CAIDA dataset (2012-2018).
For each timestamp, we generated routing trees based on these relationships. Then we calculated the chokepoint potential for every border AS per snapshot. As a result we can investigate
how countries have changed overtime in their capability to enact censorship and surveillance. This is an attempt to understand what topological trends have developed historically.
With this test we can compare nations, and see which ones have overtime increased their capability to control the flow of information across their borders.
\par
% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can easily implement censorship, it stands to reason that their might already be a negative relationship between
the chokepoint potential of a nation and its Internet freedom. If a significant relationship were to be found it would strengthen chokepoint potential as a measure of a nation's censorship capability
and it would increase the value in monitoring chokepoint potentials across the globe.
\par
We tested whether a significant relationship exists between our measure of national chokepoints and a qualitative evaluation of Internet Freedom. For Internet Freedom we used
the Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries. Each country receives a numerical score from 0 (the most free)
to 100 (the least free). We compare our results to the FOTN scores by ranking nations according to national breakthrough potential, particulary the number of border ASes required to intercept
90\% of paths for each nation and viewing these rankings against the FOTN scores.

@@

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in \figurename \ref{fig:nodesFree} and \figurename \ref{fig:nodesCensor}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Turkey) as well as the increase for other nations
(Germany and France). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.

@@

In our test of the relationship between Internet Freedom and national breakthrough potential, we plotted the Freedom on the Net score
of each nation vs the number of border ASes that that nation needed to in order to intercept 90\% of in-to-out paths. Additionally,
we evaluated the relationship with an Ordinarly Least Squares (OLS) fit, and found that the relationship was statistically significant,
with a p-value $\leq$ 0.002 for 2017. The relationship held for other timestamps as well. The results for 2017 are shown in figure \ref{fig:fotn}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotn}
	\caption{The National Breakthrough Potential (in-to-out) for nations plotted against the FOTN score
	of those nations in 2017. A higher FOTN score indicates a less free nation. Our OLS fit is also plotted.}\label{fig:fotn}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotp}
	\caption{The National Breakthrough Potential (in-to-out) for nations plotted against the FPI
	of those nations in 2017. A higher FPI indicates a less free nation. Our OLS fit is also plotted.}\label{fig:fotp}
\end{figure}

@@

\section{Conclusions and Discussion}

% Chokepoint Potential
In this paper we have introduced two novel measures, chokepoint potential, on single border ASes,
and national breakthrough potential, on entire nations, that together allow us to
evaluate the level of difficulty that a government faces when trying to censor the Internet
based entirely on AS-level topology. Our technique for evaluating AS-level topology using
\toolname{} provides a monitoring capability of BGP dynamics that was previously not possible.
We have taken advantage of efficient simulation, standard AS relationship datasets, and cross-platform
design principles so that this tool is readily deployable for future research.
% Ecolution over time
\par
Our application of \toolname{} to investigate evolution of the global AS graph over time shows us
interesting trends in AS topologies. We have identified the apparent lack of major nations to develop
more open Internet borders and gateways, despite the increasing connectivity and size of the AS graph. Additionally,
we find that the chokepoints in some nations known to conduct censorship and surveillance have increased in strength.
% Internet Freedom
\par
We have validated national breakthrough potential as having a relationship to actual censorship by showing
the significance of the relationship between the chokepoint potential of nations and the evaluations of freedom provided
by both freedom on the net and freedom of the press. This relationship implies that when censorship and surveillance are being evaluated
at the national level, it is worthwhile to consider the border AS chokepoints that are resident to the nation in question.
